This document provides the requirements and design details of the
PROJECT.  The following table (Table \ref{Table::UpdateHistory}) should be
updated by authors whenever major changes are made to the architecture
design or new components are added. Add updates to the top of the table.  
Most recent changes to the document should be seen first and the oldest 
last.

% \label{table:1}
% If you need to reference the table within your document, set a label with this command. The label will number the table and, when combined with the \ref command, will allow you to reference it.
% \ref{table:1}

\begin{longtable}{|l||p{13.5cm}|}
%\centering
\caption{Document Update History \label{Table::UpdateHistory}}\\
\hline
\textbf{Date} & \textbf{Updates} \\
\hline 
\endhead

12/10/2025 & BM:
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
\item USE FOR DEMO
\end{itemize} 
\\ \hline

12/06/2025 & JP, BM, JL, CV:
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
\item Set up an Overleaf droplet to integrate with our repository with versioning and packaging.
\end{itemize} 
\\ \hline

12/01/2025 & JP, BM, JL, CV:
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
\item Added Prometheus, Grafana, and other DevOps tools to our project to meet most of the project requirements.
\end{itemize} 
\\ \hline

11/26/2025 & JP, BM, JL, CV:
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
\item Finished an MVP of our website to prepare for integration with Digital Ocean and Docker.
\end{itemize} 
\\ \hline

11/12/2025 & JP, BM, JL, CV:
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
\item Met in the library to discuss DevOps tools and programming languages that we wanted to utilise within our project.
\end{itemize} 
\\ \hline

11/04/2025 & JP, BM, JL, CV:
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
\item Came up with a project idea and created a repository/Kanban board.
\end{itemize} 
\\ \hline

\end{longtable}


